\documentclass{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled]{berasans}
\renewcommand*\familydefault{\sfdefault}  %% Only if the base font of the document is to be sans serif
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xpatch}
\usepackage[NoDate,LabelsAligned]{currvita}
\setlength{\cvlabelskip}{
  5pt
}
\setlength{\cvlabelsep}{0.5em}
\geometry{
	a4paper,
	body={180mm,275mm},
	left=15mm,top=10mm,
	headheight=0mm,headsep=0mm,
	marginparsep=4mm,
	marginparwidth=27mm}

\newcommand{\alin}{\hskip 6mm}
\newcommand{\saut}{\vskip 2mm}

% bigger than \cdot but smaller than \bullet
\makeatletter
\newcommand*\bigcdot{$\mathpalette\bigcdot@{.5}$~}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

\newcommand{\cvitem}[1]{
\raggedright{
\vskip 3mm
\makebox[\textwidth]{\rule{11mm}{0.4pt} \hskip 2mm {\Large\bf\sc #1} \hskip 2mm \leaders \hrule \hfill}
}
}

\xpatchcmd{\cvlist}{#1}
                  {\makebox[\textwidth]{\rule{11mm}{0.4pt} \hskip 2mm {\Large\bf\sc #1} \hskip 2mm \leaders \hrule \hfill}}
                   {}{}

\begin{document}
\thispagestyle{empty}
\raggedright{
\begin{minipage}{8cm}
{\LARGE \bf Clément Geiger}
\vskip 2mm
127A St Thomas's Road, Flat 5\\
N4~2QE London\\
United Kingdom\\
{\verb clement.geiger@gmail.com }\\
\textbf{+44~(0)~7~928~533~859}
\end{minipage}}\hfill
\begin{minipage}{8cm}
\begin{flushright}
30 years old\\
French\\
\end{flushright}
\end{minipage}

\vskip 6mm

\begin{cv}{Front-end software engineer}

\vskip 3mm

\begin{cvlist}{Work experience}
    \item[2018 - present] Senior Software engineer at \textbf{Bloomberg LP}
      (London, UK), providing technical leadership to optimize the developer
      experience for a key data-processing library used across the company.

      \begin{itemize}
      \item Design and implementation of developer tools, written in TypeScript on a Chromium-based platform.
      \item Design and promotion of TypeScript APIs and their documentation.
      \item Understanding of the underlying C++ libraries and extension as needed.
      \item Close collaboration with other teams to implement a seamless developer experience across all environments where the library is used.
      \item Onboarding and mentoring of new team members (growing from 2 to 5 members)
      \end{itemize}

    \item[2015 - 2018] Software engineer at \textbf{Bloomberg LP} (London, UK),
      developing the Instant Bloomberg chat application for users of the Bloomberg
      Terminal.

      \begin{itemize}
      \item Front-end development in JavaScript on a Chromium-based platform.

      \item Practice and promotion of good software development principles; focus on
      automated testing, continuous integration to deliver a stable product.

      \item Close relationship with business and sales teams to maximize effectiveness and impact.
      \end{itemize}

    \item[2012 - 2015] Software engineer at \textbf{Aldebaran Robotics}
      (Paris, France), working on IDE and developer tools for robotic platforms.

      \begin{itemize}
      \item Desktop development in C++/Qt on all major platforms (Windows, MacOS, GNU/Linux)
      \item Focus on usability, continuously taking on user feedback and
      delivering improvements.

      \item Attention to software quality by taking testability into account during
      design, pushing for and maintaining high standards of coverage throughout
      the software's lifetime.
      \end{itemize}

    \item[2010-2012] Software engineering intern at \textbf{Philips Applied
      Technologies} (Netherlands; implemented loop and seek features in a C++ audio player), \textbf{Schlumberger} (UK; implemented a new oil reservoir simulation algorithm in C++) and
      \textbf{Gostai} (France; designed and implemented developer tools for a telepresence robot in C++/Qt).

    %\item[2012 (6 months)] Software engineer intern at \textbf{Gostai} (Paris, France)\\
     %Design and implementation of developer tools for the remote presence robot \textbf{Jazz}.

    %\item[2011 (4 months)] Software engineer intern at \textbf{Schlumberger} (Abingdon, UK)\\
     %Implementation of a new simulation algorithm for the ECLIPSE oil well simulator.

    %\item[2010 (3 months)] Software engineer intern at \textbf{Philips Applied Technologies} (Eindhoven, Netherlands)\\
     %Design and implementation of looping and seeking features on an audio player.

\end{cvlist}


\begin{cvlist}{Education and qualifications}
    \item[2011] Erasmus student exchange at \textbf{KTH} (Stockholm, Sweden)\\
    Machine learning, artificial intelligence, computational photography,
      network architecture

    \item[2007 - 2012] Master of Engineering at \textbf{INSA de Lyon}, top-tier
    engineering school\\
    Strong scientific background and specialization in computer science

    \item[2007] ``Baccalauréat scientifique'' with honours
\end{cvlist}


\begin{cvlist}{Skills}
    \item[Programming] JavaScript, TypeScript, modern C++
    \item[Libraries \& API] React, Reduce, Qt, CytoscapeJS, npm, webpack, Web Audio API (beginner)
    \item[Engineering] VCS, CI/CD, TDD
    \item[Languages] English fluent \& IT Technical, French native speaker, German beginner
\end{cvlist}


\cvitem{Interests}
\vskip -1.5mm
  \textbf{Cycling}: from everyday movement, to weekend adventures, to multi-weeks tours
  \bigcdot \textbf{Bike polo}: exactly what it sounds like
  \bigcdot \textbf{Baking}: bread, pizzas and more
  \bigcdot \textbf{Sewing}: design and fabrication of clothing items

\end{cv}
\vfill
\end{document}
